---
title: "Using CLIVARtools"
author: "Brett Longworth"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using clivartools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette serves as a brief introduction to the clivartools package.

## Installing

The package should be installed from github. You'll need the `devtools` package
installed.

```{r, eval=FALSE}
devtools::install_github("blongworth/amstools")
```
To interact with the NOSAMS DB, you'll need the odbc package installed and
a working connection to the NOSAMS database via ODBC. An ODBC connection string
should be stored in an environment variable called CONSTRING. The package has
been tested with the Microsoft MSSQL driver on Windows and Mac OS X, and with
the unixODBC and FreeTDS drivers on Linux.

If a Data Source Name (DSN) is set up within your odbc system, a CONSTRING
variable in the following format will work:

```
"DSN=database;UID=username;PWD=password"
```

This can be done from R with the `Sys.setenv` command, but this may or may not
be persistent depending on your environment.

## Getting started

First, load the library.

```{r}
library(clivartools)
```

## What cruises and stations are available?

Use getCruises and getStations to find what data to work with.

```{r eval = FALSE}
cruises <- getCruises()
cruises[1:5]

stations <- getStations(cruises[5])
stations[1:5]
```

## Get data from a profile

Use `getProfile` to get data for a profile. If `station` or `cruise` are vectors, `getProfile` will get data from all cruises/stations requested. If `station` is not given, all profiles from a cruise or cruises are returned.

```{r eval = FALSE}
data <- getProfile("A16S", 51)
head(data)
```

## Plot a profile

```{r eval = FALSE}
plotProfile(data)
```
